Results Coding

### 2023-09-08 analysis/practiceCoding_AW.Rmd
Cleaned up analysis

---
title: "Results from Primary Coding"
author: "Annie Whamond"
date: "2023-08-28"
output: html_document
---

#Prelim results and visualisations for d_journals

```{r}
#Genarate table to assess anyPPC

d_primaryONLY <- d_journals %>%
  filter(coder_id == "AW" | coder_id == "NM") %>%
  filter(journal_empirical == "Yes") %>%
  group_by(journal) %>%
  distinct(journal, .keep_all = TRUE)

 table(d_primaryONLY$sampleID, d_primaryONLY$anyPPC)

 table(d_primaryONLY$sampleID)
```

#Look at limitations for anyPPC = YES
```{r}

 d_PPConly <- d_primaryONLY %>%
   filter(anyPPC == "YES")

#Look at stated length limits
PPC_length <- d_PPConly %>%
  filter(ppc_length_A != "NO") %>%
  filter(ppc_length_A != "NOT STATED")

table(PPC_length$ppc_length_A)
table(PPC_length$ppc_length_B)

#Look at stated time limits

PPC_time <- d_PPConly %>%
  filter(ppc_time_A != "NOT STATED")

table(PPC_time$ppc_time_A)

@@

#Add COPE status
```{r}
dj_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
  slice_head(n = 108) %>%
  select(`Journal`, 'COPE' = 'COPE (T = member; F = not a member)')

dj_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`, 'COPE' = 'COPE (T = member; F = not a member)' )

dj_cope <- left_join()

#Code from checkData.RMD for extracting JIFs
d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')

journal_list_random_all <- journal_list_random_all %>%
  select(journal = Journal, WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')

journal_list_prominent_all <- journal_list_prominent_all %>%
  select(-WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')

tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))

@@

>>>>

---
title: "Results Coding"
author: "Annie Whamond"
date: "2023-08-28"
output: html_document
---
# Load processed data files
```{r}

d_journals <- read_csv(here('data','processed','d_journals.csv'))
d_articles <- read_csv(here('data','processed','d_articles.csv'))

@@

# Journal Policy Overview
```{r}

d_journals_anyPPC <- d_journals %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == "TRUE")

table(d_journals_anyPPC$sample_id)
table(d_journals_anyPPC$has_ppc)
table(d_journals_anyPPC$has_ppc, d_journals_anyPPC$sample_id)

@@

# Calculate CIs for YES 
```{r}
library(binom)

# Prominent Sample data
prominentSuccess <- 38
randomSuccess <- 23
totalSuccess <- 57

sample_size <- 100
totalSample <- 189
confidence_level <- 0.95

# Calculate the Wilson confidence interval
ci_prominent <- binom.confint(prominentSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_total <- binom.confint(totalSuccess, totalSample, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_prominent)
print(ci_random)
print(ci_total)
```
# Look at PPC names
```{r}

table(d_journals$ppc_name)

# Look at PPC length limitations
```{r}

# Removes journals that do not offer any PPC 
 d_PPConly <- d_journals %>%
   filter(has_ppc == "YES")

#Look at stated length limits
PPC_length <- d_PPConly %>%
  filter(!is.na(ppc_length)) %>%
  filter(ppc_length != "NO") %>%
  filter(ppc_length != "NOT STATED")

table(PPC_length$ppc_length, PPC_length$ppc_name)
```

# Look at PPC time limitations
``` {r}
PPC_time <- d_PPConly %>%
  filter(!is.na(ppc_time)) %>%
  filter(ppc_time != "NOT STATED")

table(PPC_time$ppc_time, PPC_time$ppc_name)

# Bar graph of PPC by COPE

```{r}
library(ggplot2)
library(RColorBrewer)

# Create bar plot
d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  ggplot() +
geom_bar(
  mapping = aes(x=has_ppc, fill = cope),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")
```
